---
title: "Q10-simple-quarto-presentation"
author: "Ty Andrews"
format:
  revealjs: 
    theme: simple
editor: visual
---

## This is my first Quarto presentation!

Here's how Quarto is described by RStudio

"Quarto® is an open-source scientific and technical publishing system built on Pandoc

-   Create dynamic content and author documents as plain text markdown or Jupyter notebooks.

-   Publish high-quality articles, reports, presentations, websites, blogs, and more.

-   Author with scientific markdown, including equations, citations, crossrefs, etc."

[Source: Quarto.org](https://quarto.org/)

## Quarto RevealJS Themes

Quarto & RevealJS combine to provide a number of themes: 

- beige, blood, dark, default, league, moon, night, serif, simple, sky, solarized

This theme is **simple**.

To set the theme put the theme name in the header as such:

```
format:
  revealjs: 
    theme: simple
```

## Plotting in slides

Using a plot generated with ggplot2 from DSCI 551 Lab 3, here is the probability density function given that a professors lectures ended **no more than 1 minute over time.**

```{r, echo=FALSE}
library(ggplot2)

lecture_time = c(0,1,1,2)
prob_dens_function = c(0,2,0 , 0)

df = data.frame(x = lecture_time, f_x = prob_dens_function)

ggplot(data=df, aes(x=lecture_time, y=prob_dens_function, group = 1)) + 
  geom_line() +
  ggtitle("PDF of Lecture End Time Given X <= 1")
```


## Code in Presentations

To show code you can either have it execute or not, you can also highlight specific lines of code like below.

First line:
```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "1"
x <- 1:10
x
LETTERS[x]
```
Second & third line:
```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "2,3"
x <- 1:10
x
LETTERS[x]
```
[Inspiration](https://www.pipinghotdata.com/posts/2022-05-12-code-line-highlighting-in-quarto-revealjs-presentations/)
